Estudio variabilidad estructural proteica

### 2016-05-13 MultipleReportAllBetas.Rmd
cambios 13/05/2016

```{r}
# Source functions.
source("FUNCTIONS/CalculateGroupsMeansQuantiles.R")

@@

}

>>>>

```{r}
# Load packages.
library(bio3d)

# Source functions.
source("FUNCTIONS/CalculateGroupsMeansQuantiles.R")

@@

# Write pdb files for MSDi.
pdbs.fname <- file.path(data.dir, paste(family, "_coordinates.pdb", sep = ""))
pdb = ReadCA(pdbs.fname, as.character(chain.p.ref))
xyz.calpha = pdb$xyz.calpha

MSDi.fit.pdb <- vec2resno(as.vector(MSDi.fit), sort(rep(1:ncol(xyz.calpha),3)))
write.pdb(xyz = c(xyz.calpha), b = MSDi.fit.pdb * 100, file = file.path(out.dir, paste(family, "_", p.ref, "_beta_", beta, ".pdb", sep = "")))

MSDi.exp.pdb <- vec2resno(as.vector(exp.smooth.norm.MSDi), sort(rep(1:ncol(xyz.calpha),3)))
write.pdb(xyz = c(xyz.calpha), b = MSDi.exp.pdb * 100, file = file.path(out.dir, paste(family, "_", p.ref, "_exp", ".pdb", sep = "")))
}

### 2016-05-13 MultipleReportAllBetas3.Rmd
cambios 13/05/2016

  exp.MSDi.quantile1 = matrix(ncol = ncol(m.exp.smooth.norm.MSDi), nrow = 1)
  exp.MSDi.quantile2 = matrix(ncol = ncol(m.exp.smooth.norm.MSDi), nrow = 1)

  for (i in (1:ncol(m.exp.smooth.norm.dr.squarei))) {
      exp.smooth.norm.dr.squarei.quantiles = as.vector(quantile((m.exp.smooth.norm.dr.squarei[, i]), probs = c(0.05, 0.95)))
      exp.smooth.norm.dr.squarei.quantile1[1, i] = exp.smooth.norm.dr.squarei.quantiles[1]
      exp.smooth.norm.dr.squarei.quantile2[1, i] = exp.smooth.norm.dr.squarei.quantiles[2]
  }

  m.mean.exp.MSDi[as.vector(all.betas == beta), 1:length(mean.exp.MSDi)] = mean.exp.MSDi
  m.exp.MSDi.quantile1[as.vector(all.betas == beta), 1:length(exp.smooth.norm.dr.squarei.quantile1)] = exp.MSDi.quantile1
  m.exp.smooth.norm.dr.squarei.quantile2[as.vector(all.betas == beta), 1:length(exp.smooth.norm.dr.squarei.quantile2)] = exp.smooth.norm.dr.squarei.quantile2

@@

  for (i in (1:n.sites.p.ref)) {
    fit = lm(exp.smooth.norm.MSDi ~ theo.smooth.norm.dr.squarei[i, 1:n.sites.p.ref] )
    MSDi.fit = fitted.values(fit)
    theo.smooth.norm.dr.squarei[i, 1:n.sites.p.ref] = MSDi.fit
  }

@@

  # Calculate groups, means and quantiles.
  theo.MSDi.group = CalculateGroupsMeansQuantiles(m.theo.smooth.norm.dr.squarei, n.mut.p, n.prot)
  mean.theo.MSDi.group = theo.MSDi.group$mean.mean.group
  theo.MSDi.group.quantile1 = theo.MSDi.group$mean.quantile1.group
  theo.MSDi.group.quantile2 = theo.MSDi.group$mean.quantile2.group
  theo.MSDi.quantile1.mean = theo.MSDi.group$quantile1.mean
  theo.MSDi.quantile2.mean = theo.MSDi.group$quantile2.mean

@@

plot(m.mean.theo.MSDi.group[1, 1:100], 
     main = "MSDi strong selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[1, 1:100], m.mean.exp.MSDi[1, 1:100]))))
lines(m.theo.MSDi.group.quantile1[1, ])
lines(m.theo.MSDi.group.quantile2[1, ])
points(m.mean.exp.MSDi[1, ], col = "red")
lines(as.vector(m.exp.MSDi.quantile1[1, ]), col = "red")
lines(as.vector(m.exp.MSDi.quantile2[1, ]), col = "red")

plot(m.mean.theo.MSDi.group[2, 1:100], 
     main = "MSDi medium selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[2, 1:100], m.mean.exp.MSDi[2, 1:100]))))
lines(m.theo.MSDi.group.quantile1[2, ])
lines(m.theo.MSDi.group.quantile2[2, ])
points(m.mean.exp.MSDi[2, ], col = "red")
lines(as.vector(m.exp.MSDi.quantile1[2, ]), col = "red")
lines(as.vector(m.exp.MSDi.quantile2[2, ]), col = "red")

plot(m.mean.theo.MSDi.group[3, 1:100], 
     main = "MSDi weak selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[3, 1:100], m.mean.exp.MSDi[3, 1:100]))))
lines(m.theo.MSDi.group.quantile1[3, ])
lines(m.theo.MSDi.group.quantile2[3, ])
points(m.mean.exp.MSDi[3, ], col = "red")
lines(as.vector(m.exp.MSDi.quantile1[3, ]), col = "red")
lines(as.vector(m.exp.MSDi.quantile2[3, ]), col = "red")

plot(m.mean.theo.MSDi.group[4, 1:100], 
     main = "MSDi no selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[4, 1:100], m.mean.exp.MSDi[4, 1:100]))))
lines(m.theo.MSDi.group.quantile1[4, ])
lines(m.theo.MSDi.group.quantile2[4, ])
points(m.mean.exp.MSDi[4, ], col = "red")
lines(as.vector(m.exp.MSDi.quantile1[4, ]), col = "red")
lines(as.vector(m.exp.MSDi.quantile2[4, ]), col = "red")

@@

plot(m.mean.theo.MSDi.group[1, 1:100], 
     main = "MSDi strong selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[1, 1:100], m.mean.exp.MSDi[1, 1:100]))))
lines(as.vector(m.theo.MSDi.quantile1.mean[1, ]))
lines(as.vector(m.theo.MSDi.quantile2.mean[1, ]))
points(m.mean.exp.MSDi[1, ], col = "red")

plot(m.mean.theo.MSDi.group[2, 1:100], 
     main = "MSDi medium selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[2, 1:100], m.mean.exp.MSDi[2, 1:100]))))
lines(as.vector(m.theo.MSDi.quantile1.mean[2, ]))
lines(as.vector(m.theo.MSDi.quantile2.mean[2, ]))
points(m.mean.exp.MSDi[2, ], col = "red")

plot(m.mean.theo.MSDi.group[3, 1:100], 
     main = "MSDi weak selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[3, 1:100], m.mean.exp.MSDi[3, 1:100]))))
lines(as.vector(m.theo.MSDi.quantile1.mean[3, ]))
lines(as.vector(m.theo.MSDi.quantile2.mean[3, ]))
points(m.mean.exp.MSDi[3, ], col = "red")

plot(m.mean.theo.MSDi.group[4, 1:100], 
     main = "MSDi no selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[4, 1:100], m.mean.exp.MSDi[4, 1:100]))))
lines(as.vector(m.theo.MSDi.quantile1.mean[4, ]))
lines(as.vector(m.theo.MSDi.quantile2.mean[4, ]))
points(m.mean.exp.MSDi[4, ], col = "red")

>>>>

  exp.MSDi.quantile1 = matrix(ncol = ncol(m.exp.MSDi), nrow = 1)
  exp.MSDi.quantile2 = matrix(ncol = ncol(m.exp.MSDi), nrow = 1)

  for (i in (1:n.sites.p.ref)) {
      exp.smooth.norm.dr.squarei.quantiles = as.vector(quantile((m.exp.smooth.norm.dr.squarei[, i]), probs = c(0.05, 0.95), na.rm = T))
      exp.MSDi.quantile1[1, i] = exp.smooth.norm.dr.squarei.quantiles[1]
      exp.MSDi.quantile2[1, i] = exp.smooth.norm.dr.squarei.quantiles[2]
  }

  m.mean.exp.MSDi[as.vector(all.betas == beta), 1:n.sites.p.ref] = exp.smooth.norm.MSDi[1:n.sites.p.ref]
  m.exp.MSDi.quantile1[as.vector(all.betas == beta), 1:length(exp.MSDi.quantile1)] = exp.MSDi.quantile1
  m.exp.MSDi.quantile2[as.vector(all.betas == beta), 1:length(exp.MSDi.quantile2)] = exp.MSDi.quantile2

@@

  for (i in (1:n.sites.p.ref)) {
    fit = lm(exp.smooth.norm.MSDi[1:n.sites.p.ref] ~ as.numeric(m.theo.smooth.norm.dr.squarei[i, 1:n.sites.p.ref]))
    MSDi.fit = fitted.values(fit)
    m.theo.smooth.norm.dr.squarei[i, 1:n.sites.p.ref] = MSDi.fit
  }

@@

  # Calculate groups, means and quantiles.
  theo.MSDi.group = CalculateGroupsMeansQuantiles(m.theo.smooth.norm.dr.squarei, n.mut.p, n.prot)
  mean.theo.MSDi.group = theo.MSDi.group$mean.mean.group[1:n.sites.p.ref]
  theo.MSDi.group.quantile1 = theo.MSDi.group$mean.quantile1.group[1:n.sites.p.ref]
  theo.MSDi.group.quantile2 = theo.MSDi.group$mean.quantile2.group[1:n.sites.p.ref]
  theo.MSDi.quantile1.mean = theo.MSDi.group$quantile1.mean[1:n.sites.p.ref]
  theo.MSDi.quantile2.mean = theo.MSDi.group$quantile2.mean[1:n.sites.p.ref]

@@

plot(m.mean.theo.MSDi.group[1, ], 
     main = "MSDi strong selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2, m.mean.exp.MSDi))))
lines(m.theo.MSDi.group.quantile1[1, ])
lines(m.theo.MSDi.group.quantile2[1, ])
points(m.mean.exp.MSDi[1, ], col = "red")
lines(as.vector(m.exp.MSDi.quantile1[1, ]), col = "red")
lines(as.vector(m.exp.MSDi.quantile2[1, ]), col = "red")

plot(m.mean.theo.MSDi.group[2, ], 
     main = "MSDi medium selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[2,], m.mean.exp.MSDi[2,]))))
lines(m.theo.MSDi.group.quantile1[2, ])
lines(m.theo.MSDi.group.quantile2[2, ])
points(m.mean.exp.MSDi[2, ], col = "red")
lines(as.vector(m.exp.MSDi.quantile1[2, ]), col = "red")
lines(as.vector(m.exp.MSDi.quantile2[2, ]), col = "red")

plot(m.mean.theo.MSDi.group[3, ], 
     main = "MSDi weak selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[3, ], m.mean.exp.MSDi[3, ]))))
lines(m.theo.MSDi.group.quantile1[3, ])
lines(m.theo.MSDi.group.quantile2[3, ])
points(m.mean.exp.MSDi[3, ], col = "red")
lines(as.vector(m.exp.MSDi.quantile1[3, ]), col = "red")
lines(as.vector(m.exp.MSDi.quantile2[3, ]), col = "red")

plot(m.mean.theo.MSDi.group[4, ], 
     main = "MSDi no selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[4, ], m.mean.exp.MSDi[4, ]))))
lines(m.theo.MSDi.group.quantile1[4, ])
lines(m.theo.MSDi.group.quantile2[4, ])
points(m.mean.exp.MSDi[4, ], col = "red")
lines(as.vector(m.exp.MSDi.quantile1[4, ]), col = "red")
lines(as.vector(m.exp.MSDi.quantile2[4, ]), col = "red")

@@

plot(m.mean.theo.MSDi.group[1, ], 
     main = "MSDi strong selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[1, ], m.mean.exp.MSDi[1, ]))))
lines(as.vector(m.theo.MSDi.quantile1.mean[1, ]))
lines(as.vector(m.theo.MSDi.quantile2.mean[1, ]))
points(m.mean.exp.MSDi[1, ], col = "red")

plot(m.mean.theo.MSDi.group[2, ], 
     main = "MSDi medium selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[2, ], m.mean.exp.MSDi[2, ]))))
lines(as.vector(m.theo.MSDi.quantile1.mean[2, ]))
lines(as.vector(m.theo.MSDi.quantile2.mean[2, ]))
points(m.mean.exp.MSDi[2, ], col = "red")

plot(m.mean.theo.MSDi.group[3, ], 
     main = "MSDi weak selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[3, ], m.mean.exp.MSDi[3, ]))))
lines(as.vector(m.theo.MSDi.quantile1.mean[3, ]))
lines(as.vector(m.theo.MSDi.quantile2.mean[3, ]))
points(m.mean.exp.MSDi[3, ], col = "red")

plot(m.mean.theo.MSDi.group[4, ], 
     main = "MSDi no selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[4, ], m.mean.exp.MSDi[4, ]))))
lines(as.vector(m.theo.MSDi.quantile1.mean[4, ]))
lines(as.vector(m.theo.MSDi.quantile2.mean[4, ]))
points(m.mean.exp.MSDi[4, ], col = "red")
